Effective Dynamic Models of Metabolic Networks

### 2016-03-23 Paper_v1.tex
new fig 1

\begin{figure}[!t]\centering
\includegraphics[width=0.35\textwidth]{./figs/Fig-1-GeneralModel-Results.pdf}
\caption{HCM-FBA proof of concept metabolic study.
A: Prototypical network with six metabolites and seven reactions.
Intracellular cellmass precursors $A,B$ and $C$ are balanced (no accumulation) while the extracellular metabolites ($A_{e},B_{e}$ and $C_{e}$) are not balanced (can accumulate).
The oval denotes the cell boundary, $q_{j}$ is the jth flux across the boundary and $v_{k}$ denotes the kth intracellular flux.
B: Simulation of extracellular metabolite trajectories using HCM-FBA (solid line) versus HCM-EM (points) for the proof of concept metabolic network.
}\label{fig:model-fitting}
\end{figure}

>>>>

\begin{figure}[!t]\centering
\includegraphics[width=0.45\textwidth]{./figs/Fig-1-Method-General.pdf}
\caption{HCM proof of concept metabolic study.
A: HCM is formulated to split the uptake flux among different pathways (defined as modes) to satisfy some chosen metabolic objective.
HCM-EM considers all possible modes within a network, whereas HCM-FBA combines modes by FBA.
B: Prototypical network with six metabolites and seven reactions.
Intracellular cellmass precursors $A,B$ and $C$ are balanced (no accumulation) while the extracellular metabolites ($A_{e},B_{e}$ and $C_{e}$) are not balanced (can accumulate).
The oval denotes the cell boundary, $q_{j}$ is the jth flux across the boundary and $v_{k}$ denotes the kth intracellular flux.
C: Simulation of extracellular metabolite trajectories using HCM-FBA (solid line) versus HCM-EM (points) for the proof of concept metabolic network.
}\label{fig:model-fitting}
\end{figure}
